Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-01-29 paper.tex
Item 29: Fixed description of inductive stirrer
Item 32: Changed references to CPE in conclusion

Faradaic measurements were made using an Agilent E5270B Precision Measurement Mainframe producing a stepped DC voltage stimulus across electrodes 2 and 6 whilst continuously measuring the output current. We commenced with 1.0X concentration of the stock solution (table~\ref{tab:PBSrecipe}). This solution was progressively diluted in factors of two between each measurement. The solution was mixed continuously by inductive stirrer and the electrode remained submerged throughout the entire process.
A single measurement run involved stepping the voltage across electrodes 2 and 7 from 0.5\thinspace V to 1.2\thinspace V in increments of 0.05\thinspace V; this range was previously determined to capture the onset of Faradaic conduction.

@@

We have used the parameters of a compact electrical model of an implantable electrode as a way of objectively comparing scenarios.
We have measured how changing the concentration of PBS affects the parameters.
We have drawn direct relationships with concentration sufficient to predict interface characteristics at arbitrary dilutions of PBS.
We found that the CPE moves much more slowly with concentration whereas the resistance moved almost linearly.
Using DC measurements we conclude that the salinity of the bulk does not affect Faradaic conduction until a threshold voltage is reached. We hypothesise that this is because the CPE is setting the effective concentration of ions in a localised volume surrounding each electrode. In-vivo measurements of the CPE in sheep spine showed that no single concentration of PBS matches both the CPE and the resistive characteristics at once. Nevertheless, 0.1X PBS is a good compromise.

>>>>

Faradaic measurements were made using an Agilent E5270B Precision Measurement Mainframe producing a stepped DC voltage stimulus across electrodes 2 and 6 whilst continuously measuring the output current. We commenced with 1.0X concentration of the stock solution (table~\ref{tab:PBSrecipe}). This solution was progressively diluted in factors of two between each measurement. The solution was mixed continuously using a standard laborotary grade magnetic stirrer and the electrode remained submerged throughout the entire process.
A single measurement run involved stepping the voltage across electrodes 2 and 7 from 0.5\thinspace V to 1.2\thinspace V in increments of 0.05\thinspace V; this range was previously determined to capture the onset of Faradaic conduction.

@@

We have used the parameters of a compact electrical model of an implantable electrode as a way of objectively comparing scenarios.
We have measured how changing the concentration of PBS affects the parameters of this model.
We have drawn direct relationships with concentration sufficient to predict interface characteristics at arbitrary dilutions of PBS.
We found that the magnitude of the CPE element moves much more slowly with concentration whereas the resistance moved almost linearly.
Using DC measurements we conclude that the salinity of the bulk does not affect Faradaic conduction until a threshold voltage is reached. We hypothesise that this is because the double-layer sets the effective concentration of ions in a localised volume surrounding each electrode. In-vivo measurements of platinum electrodes in sheep spine showed that no single concentration of PBS matches both the CPE and the resistive characteristics at once. Nevertheless, 0.1X PBS is a good compromise.
